Notes on the Mohri-Rostamizadeh approach

### 2015-06-01 scratch/mohri-notes.tex
Copied files from svn

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% PACKAGES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{latexsym}
\usepackage{fullpage}
\usepackage{amsmath}
\usepackage{amssymb}
%\usepackage{mathtools}
\usepackage{enumerate}
\usepackage{accents}
\usepackage{tikz}
%\usepackage{pgfplots}
\usepackage[ruled]{algorithm}
\usepackage{algpseudocode}
\usepackage{dsfont}
\usepackage[bf]{caption}
\usepackage{hyperref}
\hypersetup{
    bookmarks=true,         % show bookmarks bar?
    unicode=false,          % non-Latin characters in Acrobats bookmarks
    pdftoolbar=true,        % show Acrobats toolbar?
    pdfmenubar=true,        % show Acrobats menu?
    pdffitwindow=false,     % window fit to page when opened
    pdfstartview={FitH},    % fits the width of the page to the window
    pdftitle={My title},    % title
    pdfauthor={Author},     % author
    pdfsubject={Subject},   % subject of the document
    pdfcreator={Creator},   % creator of the document
    pdfproducer={Producer}, % producer of the document
    pdfkeywords={keyword1} {key2} {key3}, % list of keywords
    pdfnewwindow=true,      % links in new window
    colorlinks=true,       % false: boxed links; true: colored links
    linkcolor=red,          % color of internal links (change box color with linkbordercolor)
    citecolor=blue,        % color of links to bibliography
    filecolor=magenta,      % color of file links
    urlcolor=cyan           % color of external links
}
\usepackage{amsthm}
\usepackage{times}
\usepackage{natbib}
\usepackage{nicefrac}
\usepackage{wrapfig}
\usepackage[capitalize]{cleveref}

@@

\newcommand{\paren}[1]{\left( #1 \right)}
\newcommand{\sqprn}[1]{\left[ #1 \right]}
\newcommand{\tlprn}[1]{\left\{ #1 \right\}}
%\newcommand{\set}[1]{\left\{ #1 \right\}}
\newcommand{\oo}[1]{\frac{1}{#1}}
\newcommand{\nrm}[1]{\left\Vert #1 \right\Vert}
\newcommand{\tnrm}[1]{\Vert #1 \Vert}
\newcommand{\abs}[1]{\left| #1 \right|}
\newcommand{\trn}{^\intercal} %operator transpose

@@

\title{Aryeh's scratch notes}
%\author{Daniel, Aryeh, Csaba}

@@

%\begin{abstract}
%An abstract
%\end{abstract}
\newcommand{\XX}{\mathbb{X}}
\newcommand{\one}[1]{\mathbb{I}\left\{#1\right\}}
\newcommand{\N}{\mathbb{N}}
For any $\mu,a$ such that $n = 2\mu a$ and $\delta>2(\mu-1)\beta(a)$,
with probability at least $1-\delta$,
\begin{align}
\label{eq:xbound}
|\bar{X}_n - \EE{f(X_1)}|
\le c_1\sqrt{\frac{1}{\mu}} + c_2\sqrt{\frac{\ln(2/\delta')}{2\mu}}\,,
\end{align}
where $\delta'=\delta-2(\mu-1)\beta(a)$
If $\beta(k)$ denotes the $k$th $\beta$-mixing coefficient of $(X_i)$ then 
\begin{align}
\label{eq:betabound}
 \beta(k) \le \oo{\pi_*}e^{-k \gamma_*}
\end{align}
where  $\gamma_* = 1-\lambda_*$ is the spectral gap ($\lambda_*$ is the second largest eigenvalue of $T$)
and  $\pi_*  = \min_i \pi_i>0$ is the critical probability underlying the chain
(see the $\beta$-mixing note).
For a given value of $\pi_*,\gamma_*$, $\delta$, let $B_n(\pi_*,\gamma_*,\delta)$ be the optimal value of the optimization problem
\begin{align*}
\lefteqn{ \min_{\mu,a} \min\left(1, 
c_1\sqrt{\frac{1}{\mu}} + c_2\sqrt{\frac{\ln(2/\delta')}{2\mu}}\right) 
} \\
& \qquad \text{s.t.} \quad n = 2\mu a, \quad \delta>2(\mu-1)\oo{\pi_*}e^{-a \gamma_*},
\quad \delta' = \delta-2(\mu-1)\oo{\pi_*}e^{-a \gamma_*}, \quad \mu,a \in \N\,.
\end{align*}

\paragraph{We will upper-bound} $B_n$ as follows.
Choose
$$ a=(2\ln n)/\gamma_*.$$
Then
$\mu=n/2a=\gamma_*n/4\ln n$
and
\beq
\delta' &=& \delta-2(\mu-1)\oo{\pi_*}e^{-a \gamma_*} \\
&=& \delta - 2\paren{\frac{\gamma_*n}{4\ln n}-1}\oo{n^2\pi_*} \\
%&=& \delta - {\frac{\gamma_*}{2\pi_*n\ln n}} + O(n^{-2}) \\
&=&
\delta - \sqprn{
\frac{\gamma_*}{2\pi_*n\ln n}-\frac{2}{\pi_*n^2}
}
=:\delta-x.
%\frac{2}{\delta'}
%&=&
%\frac{2}{\delta} + 
\eeq
Now
\beq
\ln\frac{2}{\delta-x} &=& \ln\frac{2}{\delta}+\frac{x}{\delta^2}+O(x^2), \\
\sqrt{\ln\frac{2}{\delta-x}} &=& 
\sqrt{\ln\frac{2}{\delta}}
+
\frac{x}{2\delta\sqrt{\ln(2/\delta)}}+O(x^2), \\
\eeq
and hence,
\beq
B_n(\pi_*,\gamma_*,\delta)
&\le&
2\sqrt{\frac{\ln n}{\gamma_*n}}
\sqprn{
c_1
+ c_2
\sqrt{\ln(2/\delta')/2}
}\\
&=&
2\sqrt{\frac{\ln n}{\gamma_*n}}
\sqprn{
c_1
+ c_2
\paren{
\sqrt{
\oo2
\ln\frac{2}{\delta}}
+
\frac{x}{2\delta\sqrt{2\ln(2/\delta)}}+O(x^2)
}
}\\
&=&
2\sqrt{\frac{\ln n}{\gamma_*n}}
\sqprn{
c_1
+ c_2
\paren{
\sqrt{\oo2\ln\frac{2}{\delta}}
+
\frac{
\gamma_*
}{4{\pi_*n\ln n}\delta\sqrt{2\ln(2/\delta)}}+O(n^{-2})
}
}\\
&=&
2c_1\sqrt{\frac{\ln n}{\gamma_*n}}
+
2c_2\sqrt{\frac{\ln n}{2\gamma_*n}
\ln\frac{2}{\delta}}
+
c_2\frac{\sqrt{\gamma_*}}
{2\pi_* n^{3/2}\delta\sqrt{2\ln(n) \ln(2/\delta)}}
+
\tilde O(n^{-2.5}).
\eeq

\paragraph{Estimating the bias in $\hat T_{ij}$.}
This analysis assumes stationarity. 
For $1\le i,j\le d$, define the random variable $N_{ij}=\#(i,j)$ to be the number of consecutive $(i,j)$
pairs in the observed sequence; define $N_i=\#(i)$ analogously.
We have
\beq
\hat T_{ij} = \frac{ N_{ij}}{N_i}.
\eeq
We will estimate the bias $\E[\hat T_{ij}]-T_{ij}$ as follows.
First, compute the expectations of the numerator and the denominator:
\beq
\E[N_{ij}]
&=& 
(n-1)\pi_i T_{ij} 
\\
\E[N_{i}]
&=& n\pi_i
,\\
\frac{\E[N_{ij}]}{\E[N_{i}]}
&=&
\frac{(n-1)\pi_i T_{ij}}{n\pi_i} = T_{ij}+O\paren{\oo n}.
\eeq
To estimate $\E[\hat T_{ij}]$, we are going to claim that both the numerator and the denominator
are concentrated about their means.
In particular, both $N_{ij}$ and $N_i$ are Lipschitz (w.r.t. Hamming) functions of the state sequence
(with constants $2$ and $1$, resp.),
and hence, invoking \citet[Theorem 1.1]{meroi2012-jap} with $G=1/\pi_*$ and $\theta=e^{-\gamma_*}$,
\beq
\P{ \abs { 
%\oo n\E[N_{ij}] - (1-\oo n)\pi_i T_{ij} 
N_{ij}-\E[N_{ij}]
} > \eps n
} &\le& 2\exp\paren{ -\frac{n(1-e^{-\gamma_*})^2\pi_*^2\eps^2}{8} } \\
\P{ \abs { 
%\oo n\E[N_i] - \pi_i  
N_{i}-\E[N_{i}]
} > 
\eps n} &\le& 2\exp\paren{ -\frac{n(1-e^{-\gamma_*})^2\pi_*^2\eps^2}{2} } \\
\eeq
Thus, with probability at least
\beq
1-\delta &:=& 1-4 \exp\paren{ -\frac{n(1-e^{-\gamma_*})^2\pi_*^2\eps^2}{8} },
\eeq
%all of 
the empirical counts $N_{ij}$ and $N_i$ are $\eps n$-close to their expectations.
Finally, since for all $a,b,x>0$, we have
\beq
\abs{ \frac{a\pm x}{b\pm x} - \frac a b} \le \frac{a+b}{b^2}x+O(x^2), 
\eeq
it follows that for all $i,j$,
\beq
\abs{
\E\sqprn{\frac{ N_{ij}}{N_i}}
-
\frac{\E[N_{ij}]}{\E[N_{i}]}
}
&\le&
\delta + \frac{\E[N_{ij}]+\E[N_i]}{\E[N_i]^2}\eps + O(\eps^2) \\
&=& \delta + \frac{ (n-1)\pi_i T_{ij} + n\pi_i}{n^2\pi_i^2}\eps + O(\eps^2) \\
&\le& \delta + \frac{ (1-1/n)T_{ij} + 1}{n\pi_*}\eps + O(\eps^2).
\eeq

Thus,
\beq
\abs{\E[\hat T_{ij}]-T_{ij}} &\le&
%\delta + \frac{ (1-1/n)T_{ij} + 1}{n\pi_*}\eps + O\paren{\eps^2+\oo n}.
O\paren{
\exp\paren{ -\frac{n(1-e^{-\gamma_*})^2\pi_*^2\eps^2}{8} }
+\frac{\eps}{n\pi_*}}.
\eeq
Choosing $\eps=O\paren{\frac{1}{\pi_*(1-e^{-\gamma^*})\sqrt{n\ln n}}}$ yields
\beq
\abs{\E[\hat T_{ij}]-T_{ij}} &\le&
O\paren{
\frac{1}{\pi_*^2(1-e^{-\gamma^*})n\sqrt{n\ln n}}}.
\eeq

\paragraph{Stationariy assumption:}
One approach is to let the chain run for some time to ``burn in'',
until it reaches the distribution $\pi'$. If $\pi$ is the true stationary distribution,
then all of our ``w.h.p.'' results will hold with an additive correction of 
$\tvnorm{\pi-\pi'}$. The problem is that we won't know for how long to burn in
and also won't know $\tvnorm{\pi-\pi'}$ --- a chicken and egg problem.

Another idea is to use ``coupling from the past'':\\
\url{http://www.cc.gatech.edu/~vigoda/MCMC_Course/CouplingFromPast.pdf}
\\
\url{http://people.csail.mit.edu/costis/6896sp11/lec8s.pdf}
\\
This requires multiple restarts but otherwise works well with finite state spaces.
It gives us guaranteed perfect samples from the stationary distribution,
and from that point the chain can be run for $n$ steps to obtain our statistics.

\paragraph{Still need to do:}
Analytic upper bound on $\EE{ \hat{B}_n(\delta)}$.
Matching lower bound.

@@

Thus, we need estimates of $\gamma_*$ and $\pi_*$.
To estimate them we may want to estimate the stationary probabilities and the transition matrix $T$.
Let $\hat \pi$ denote the estimate of the former, while let $\hat T$ be the estimate of the latter.
In particular, $\hat \pi_i$ is taken to be the empirical frequency of the visits of state $i$ in $(X_t)$,
while we let $\hat T_{i,j}$ the frequency when 
$X_{t+1}=j$ happens given that $X_t = i$ ($t=1,\dots,n-1$). 
When $X_t = i$ never happens, we take $\hat T_{i,\cdot}$ to be the uniform distribution.
Since $\Prob{\sum_{t=1}^n \one{X_t = i}=0}=\Prob{X_1\ne i, \dots, X_n\ne i}>0$ for each $i$, $\hat T_{ij}$ is a biased estimate of $T_{ij}$, although the bias decreases exponentially fast.

For $x\in \R^d$, let $D_x$ be the diagonal matrix with $x$ in its diagonal. 
Define $L = D_\pi^{-1/2} T  D_\pi^{1/2}$, $\hat{L} = D_{\hat{\pi}}^{-1/2} \hat{T} D_{\hat{\pi}}^{1/2}$, 
By Weyl's inequality (see notes.pdf),
\begin{align}
\label{eq:gammabound}
|\hat{\gamma}_* - \gamma_* | = |\hat{\lambda}_* - \lambda_* | \le \tnrm{\hat L - L }_2
\end{align}
and so it remains to bound this latter quantity.
Define $E_T = D_{\pi}^{-1/2} (\hat T - T ) D_{\pi}^{1/2}$
and $E_\pi = D_{\hat{\pi}}^{-1/2} D_\pi^{1/2} - I$.
We have (see notes.pdf),
\begin{align}
\label{eq:lbound}
\tnrm{\hat L - L}_2 \le \norm{E_T}_2 + \norm{E_{\pi}}_2 (\norm{E_T}_2+1) (\norm{E_\pi}_2+2)\,.
\end{align}
Now, $\norm{E_T}_2 = \tnrm{\hat T - T}_2$ (because the eigenvalues of $E_T$ are the same as that of $\hat T - T$).
Further, for any $\mu,a$ such that $n=2\mu a$
and $\delta>2(\mu-1)\beta(a)$,
with probability at least $1-\delta$,
\begin{align}
\label{eq:tbound}
\tnrm{T-\hat T}_2
\le 25\sqrt{\frac{d}{\mu}} + 2\sqrt{\frac{\ln(2/\delta')}{2\mu}}\,,
\end{align}
where $\delta'=\delta-2(\mu-1)\beta(a)$ (see mohri-notes.pdf). \todoc{This does not take into account the bias.}
\todoc[inline]{Next problem: For a fixed $n$, this will limit the range of $\delta$.
For any $n$, there will be a range of $\delta$ in the neighbourhood of $0$ for which the algorithm
will need to return ``I don't know''.
}
Similarly, for any $\mu',a'$ such that $n=2\mu' a'$
and $\delta>2(\mu'-1)\beta(a')$,
with probability at least $1-\delta$,
\begin{align}
\label{eq:pibound}
|\hat\pi_i - \pi_i | \le C \left( \sqrt{\frac{d}{\mu'}} + \sqrt{\frac{\ln(2/\delta'')}{2\mu'}}\right)\,,
\end{align}
where $\delta''=\delta-2(\mu'-1)\beta(a')$.

By combining~\eqref{eq:betabound},
\eqref{eq:gammabound}, \eqref{eq:lbound}, \eqref{eq:tbound} and~\eqref{eq:pibound}, we can derive 
that for any $0\le \delta \le 1$,
 $\mu,a,\mu',a'$  such that $n = 2\mu a$ and
 $\frac{2}{\pi_*} \max( (\mu-1)e^{-a\gamma_*}, (\mu'-1)e^{-a'\gamma_*} )<\delta$, 
with probability $1-\delta$,
\begin{align*}
|\hat{\gamma}_* - \gamma_* | &\le u( \gamma_*, \pi_*, \hat{\gamma}, \hat\pi, \hat T, n, \mu, a, \mu', a', \delta )\,,\\
|\hat{\pi}_* - \pi_* | &\le v( \gamma_*, \pi_*, \hat{\gamma}, \hat\pi, \hat T, n, \mu, a, \mu', a', \delta )\,,
\end{align*}
for some functions $u$ and $v$.
Reordering (and relaxing) the  inequalities we get
\begin{align*}
\gamma_* &\ge \hat\gamma_* - u( \gamma_*, \pi_*, \hat{\gamma}, \hat\pi, \hat T, n, \mu, a, \mu', a', \delta )\,,\\
 \pi_*  &\ge \hat{\pi}_* - v( \gamma_*, \pi_*, \hat{\gamma}, \hat\pi, \hat T, n, \mu, a, \mu', a', \delta )\,.
\end{align*}
Now, let $\hat{B}_n(\delta)$ be the optimal value of the optimization problem 
\begin{align*}
\lefteqn{\max B_n(g,p,\delta)\qquad \text{s.t.} }\\
&\qquad  g \ge \hat\gamma_* - u( g, p, \hat{\gamma}, \hat\pi, \hat T, n, \mu, a, \mu', a', \delta )\,,\\
&\qquad p  \ge \hat{\pi}_* - v( g, p, \hat{\gamma}, \hat\pi, \hat T, n, \mu, a, \mu', a', \delta )\,,\\
&\qquad n = 2\mu a, \quad n = 2\mu' a'\,,\\
&\qquad \frac{2}{p} \max( (\mu-1)e^{-ag}, (\mu'-1)e^{-a'g} )<\delta\,,\\
&\qquad g,p >0, \mu,a,\mu',a'\in \N\,.
\end{align*}
Then, w.p. $1-\delta$, it holds that
\[
|\bar{X}_n - \EE{f(X_1)}| \le \hat{B}_n(\delta)\,.
\]

Next goals: Analytic upper bound on $\EE{ \hat{B}_n(\delta)}$.
Matching lower bound.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% PACKAGES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{latexsym}
\usepackage{fullpage}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{mathtools}
\usepackage{enumerate}
\usepackage{accents}
\usepackage{tikz}
\usepackage{pgfplots}
\usepackage[ruled]{algorithm}
\usepackage{algpseudocode}
\usepackage{dsfont}
\usepackage[bf]{caption}
\usepackage{hyperref}
\hypersetup{
    bookmarks=true,         % show bookmarks bar?
    unicode=false,          % non-Latin characters in AcrobatÕs bookmarks
    pdftoolbar=true,        % show AcrobatÕs toolbar?
    pdfmenubar=true,        % show AcrobatÕs menu?
    pdffitwindow=false,     % window fit to page when opened
    pdfstartview={FitH},    % fits the width of the page to the window
    pdftitle={My title},    % title
    pdfauthor={Author},     % author
    pdfsubject={Subject},   % subject of the document
    pdfcreator={Creator},   % creator of the document
    pdfproducer={Producer}, % producer of the document
    pdfkeywords={keyword1} {key2} {key3}, % list of keywords
    pdfnewwindow=true,      % links in new window
    colorlinks=true,       % false: boxed links; true: colored links
    linkcolor=red,          % color of internal links (change box color with linkbordercolor)
    citecolor=blue,        % color of links to bibliography
    filecolor=magenta,      % color of file links
    urlcolor=cyan           % color of external links
}
\usepackage{amsthm}
\usepackage{times}
\usepackage{natbib}
\usepackage{nicefrac}
\usepackage{wrapfig}
\usepackage[capitalize]{cleveref}

@@

\newcommand{\paren}[1]{\left( #1 \right)}
\newcommand{\sqprn}[1]{\left[ #1 \right]}
\newcommand{\tlprn}[1]{\left\{ #1 \right\}}
%\newcommand{\set}[1]{\left\{ #1 \right\}}
\newcommand{\oo}[1]{\frac{1}{#1}}
\newcommand{\nrm}[1]{\left\Vert #1 \right\Vert}
\newcommand{\abs}[1]{\left| #1 \right|}
\newcommand{\trn}{^\intercal} %operator transpose

@@

\title{Notes on the Mohri-Rostamizadeh approach}
%\author{Daniel, Aryeh, Csaba}

@@

%\begin{abstract}
%An abstract
%\end{abstract}

Let $T$ be the true transition matrix and $\hat T$ the estimated one
(leaving the estimation method presently unspecified). 
Recall that for any matrix $A$, its Euclidean norm $\nrm{A}_2$ is given by
$$ \nrm{A}_2 = \sup_{\nrm{x}\le1}\nrm{Ax} 
= \sup_{\nrm{x},\nrm{y}\le1}x\trn A y,
$$
where all vector norms are $\ell_2$ unless stated otherwise.

We are interested
in bounding
$$ \nrm{T-\hat T}_2 = \sup_{\nrm{x},\nrm{y}\le1} {x\trn(T-\hat T)y} .
$$

Trying to stay notationally close to \cite{mohri-rosta08},
let $H=B\times B$,
where $B$ is the Euclidean unit ball, and put
$R(x,y)=x\trn T y$, $\hat R_S(x,y)=x\trn \hat T y$.
Then
$$ \nrm{T-\hat T}_2 = \sup_{(x,y)\in H} R(x,y)-\hat R_S(x,y)=:\Phi(S),$$
where $S$ is the observed sample sequence.

We will need an analogue of Prop. 1 in \cite{mohri-rosta08}:
$$R(x,y) = \E_{S}[\hat R_S(x,y)].$$
I believe that for $S$ sampled from a stationary process
and $\hat T_{ij}$ taken to be the sample mean, this indeed holds.
\todoc{I don't think so. There is a bias because maybe $i$ is never visited.}
I don't think it holds for the median-of-means estimate.

[Note: there appears to be something wrong with the indexing
of the blocks in (6)-(7) of \cite{mohri-rosta08}. 
The numbering in 
\cite{MR1258867}, p.101 makes more sense, and we will follow it.]
Partition the sequence $S=(z_1,\ldots,z_n)$,
$n=2a\mu$, into $2a\mu$ blocks of length $a$.
Let $S_0$ be the sequence of odd blocks
and $\tilde S_0$ a sequence of independent blocks of length
$a$, where each block in $\tilde S_0$ is distributed identically to its
corresponding block $S_0$.

Since $\abs{\Phi(\cdot)}\le2$, Lemma 4.1 of
\cite{MR1258867} implies
$$ \abs{ \E_{S_0}[\Phi]-\E_{\tilde S_0}[\Phi]}\le 2(\mu-1)\beta(a),$$
where $\beta(\cdot)$ is the beta-mixing coefficient.

By Lemma 1 of \cite{mohri-rosta08}, we have,
for all $a,\mu,\eps>0$ with $2\mu a=n$ 
%and 
%$\eps>\E_{\tilde S_0}[\Phi(\tilde S_0)]$,
that
$$ \P{\Phi(S)>\eps}
\le 2\P{ \Phi(\tilde S_0)
%-\E_{\tilde S_0}[\Phi(\tilde S_0}]
>\eps
}
+
2(\mu-1)\beta(a).
$$

Proposition 2 ibid. yields, for all
$\eps>\E_{\tilde S_0}[\Phi(\tilde S_0)]$,

$$ \P{\Phi(S)>\eps} \le
2\exp(-\mu{\eps'}^2/2)+2(\mu-1)\beta(a),
$$
where $\eps'=\eps-\E_{\tilde S_0}[\Phi(\tilde S_0)]$.

Now invoke Lemma 2 ibid. to bound the expectation over iid blocks:
$$ \E_{\tilde S_0}[\Phi(\tilde S_0)] \le \calR_\mu(H),$$
where $\cal_\mu(\cdot)$ is the ordinary (iid) Rademacher complexity of
$H$.
Now it is well-known \cite{MR1965359} that the $\ell_2$
$t$-covering number of the $d$-dimensional Euclidean unit ball is
bounded by $(3/t)^d$. 
To bound the $\ell_2$ covering number of $H=B_d\times B_d$,
fix a radius $t$ and
%recall that
%$$ 
%%\frac{\sqrt{a}+\sqrt{b}}{\sqrt 2}
%%\le 
%\sqrt{a+b}\le \sqrt a+\sqrt b$$
%for all $a,b>0$.
%Hence
observe that
\beq
\nrm{(x,y)}_2 &=& \sqrt{ \sum_i x_i^2 + \sum_j y_j^2} \\
&\le& \sqrt2 t.
\eeq
Hence,
$$ B_d\times B_d \subset \sqrt2 B_{2d} $$
and $H$
can be covered by
$(\sqrt 6/t)^{2d}$ balls of radius $t$.
Using Dudley's chaining integral to estimate
the Rademacher complexity, we have

\beq
\calR_\mu(H) &\le& \frac{12}{\sqrt\mu}\int_0^{\sqrt2}\sqrt{d\ln(\sqrt 6/t)}dt \\
&\le& 25\sqrt{d/\mu}.
\eeq
Note that $d$ is the number of states, consistent with our other notes.

Adapting Theorem 1 in \cite{mohri-rosta08} to our needs, we have
that for any sample $S$ of length $n=2\mu a$
and $\delta>2(\mu-1)\beta(a)$,
the following
holds with probability at least $1-\delta$:
\beq
%\Phi(S) 
\nrm{T-\hat T}_2
\le 25\sqrt{\frac{d}{\mu}} + 2\sqrt{\frac{\ln(2/\delta')}{2\mu}},
\eeq
where $\delta'=\delta-2(\mu-1)\beta(a)$.

Recall that our other calculation (``beta-mixing'') gave
$$ \beta(a) \le \oo{\pi_*}e^{-a(1-\lambda_2)}.$$

@@
